Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2022-01-26 prevalence_testing/manual.tex
addition of unemployment results

 The input for this function is
\begin{itemize}
	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+2$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$. 
	\item \texttt{Y} is a list of responses with length $n +1$,  where the first element of the list should be the response of the time series of interest and the remaining elements of the list are the responses of the donors. It should be a vector.  Note  that to compute the lag, the effective sample size used is $T_i - 1$, where $T_i$ is the time series length of $i$th time series.
	\item \texttt{X} is a list of covariates with length $n+1$, where the first element of the list should be the covariates of the time series of interest and the remaining elements of the list are the covariates of the donors. The covariates should be in the class of \texttt{matrix} with size $T_i\times p$ for $i = 1, \ldots, n+1$. Note that the sample size of each element  in \texttt{X} should be  $T_i+ K_i + H$, where $K_i$ is the training sample size and $T_i$ is the length of the donor time series that are wished to be considered as the data used in forecast comparison. $H$ is the maximum horizon.
	\item \texttt{K} is a vector of training sample sizes that are used to compute $h$-step forecast for each data point. \texttt{K} has a length of $n+1$. If \texttt{retro = FALSE}, \texttt{K[1]} can be \texttt{NA}.
	\item \texttt{H} is the maximum $h$ that an $h$-step forecast that is wished to be considered in the multi-horizon forecast comparison testing procedure in \citeA{quaedvlieg2021multi}.
	\item \texttt{Ts} is a vector of length $n+1$, and it specifies the length of the time series (ordered from the time series of interest to donors). Note that for each element of \texttt{Ts}, it should be at least greater than or equal to $K_i + H + 2$.
	\item \texttt{ell} is the block length of the moving block bootstrap. See details in \texttt{taSPA.mhfc}.
	\item \texttt{B} is the bootstrap sample size. See details in \texttt{taSPA.mhfc}.
	\item \texttt{bw} is the bandwidth of computation for HAC estimator. See details in \texttt{taSPA.mhfc}.
	\item \texttt{sig.levl} is the significance level for the test. It is 0.05 in default.
	\item \texttt{retro} is a logical value indicating \texttt{TRUE} or \texttt{FALSE}. If  \texttt{TRUE}, the $p$-value for the time series of interest will be computed. If  \texttt{FALSE}, only the $p$-values of donors will be computed. This argument is intended for retrospective data analysis where the $p$-value of the time series of interest is needed.
	\item \texttt{scale} option can allow users to compute weights based on scaled covariates or not. See details in \texttt{scm}.
\end{itemize}

>>>>

 The input for this function is
\begin{itemize}
	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+2$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$. 
	\item \texttt{Y} is a list of responses with length $n +1$,  where the first element of the list should be the response of the time series of interest and the remaining elements of the list are the responses of the donors. It should be a vector.  Note  that to compute the lag, the effective sample size used is $T_i - 1$, where $T_i$ is the time series length of $i$th time series.
	\item \texttt{X} is a list of covariates with length $n+1$, where the first element of the list should be the covariates of the time series of interest and the remaining elements of the list are the covariates of the donors. The covariates should be in the class of \texttt{matrix} with size $T_i\times p$ for $i = 1, \ldots, n+1$. Note that the sample size of each element  in \texttt{X} should be  $T_i+ K_i + H$, where $K_i$ is the training sample size and $T_i$ is the length of the donor time series that are wished to be considered as the data used in forecast comparison. $H$ is the maximum horizon.
	\item \texttt{K} is a vector of training sample sizes that are used to compute $h$-step forecast for each data point. \texttt{K} has a length of $n+1$. If \texttt{retro = FALSE}, \texttt{K[1]} can be \texttt{NA}.
	\item \texttt{H} is the maximum $h$ that an $h$-step forecast that is wished to be considered in the multi-horizon forecast comparison testing procedure in \citeA{quaedvlieg2021multi}.
	\item \texttt{Ts} is a vector of length $n+1$, and it specifies the length of the time series (ordered from the time series of interest to donors). Note that for each element of \texttt{Ts}, it should be at least greater than or equal to $K_i + H + 2$.
	\item \texttt{ell} is the block length of the moving block bootstrap. See details in \texttt{taSPA.mhfc}.
	\item \texttt{B} is the bootstrap sample size. See details in \texttt{taSPA.mhfc}.
	\item \texttt{bw} is the bandwidth of computation for HAC estimator. See details in \texttt{taSPA.mhfc}.
	\item \texttt{sig.levl} is the significance level for the test. It is 0.05 in default.
	\item \texttt{retro} is a logical value indicating \texttt{TRUE} or \texttt{FALSE}. If  \texttt{TRUE}, the $p$-value for the time series of interest will be computed. If  \texttt{FALSE}, only the $p$-values of donors will be computed. This argument is intended for retrospective data analysis where the $p$-value of the time series of interest is needed.
	\item \texttt{scale} option can allow users to compute weights based on scaled covariates or not. See details in \texttt{scm}.
	\item \texttt{sc.x} is a list of one vector and a list, where the ordering matters. The first vector should be a vector of indices referring to which time series wish to consider additional covariates that are present in the models but not considered in the weight computation. The second list should be a list of matrices with length equal to the length of the first vector. The matrices are the matrices of covariates, which are present in the models but not considered in the weight computation.
\end{itemize}

### 2022-01-26 prevalence_testing/postshocktest2021draft.tex
addition of unemployment results

>>>>

\section{Testing shock prevalence for persons on nonfarm payrolls}

\begin{table}[H]
	\caption{Results for persons on nonfarm payrolls ($n=4$), $\mbf{W}^* = (0, 0, 0, 1)$ from scaled covariates} \label{uemtable}
\begin{center}
  \begin{tabular}{ccccccccr}
      Model & weighted  AIC & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     $\mc{M}_1$  & $-655.03$ & 0  & 1 & 0 (No) &1 (No)  \\      
      $\mc{M}_2$  & $-660.14$ & 1 & $0.19$   & 0 (Yes) &0 (Yes)   \\[.2cm]
  \end{tabular}
\end{center}	
\end{table}

\begin{figure}[H]
	\begin{center}
		\includegraphics[height = 8cm]{UEMtransience.pdf}
		\caption{The shock transience of $\{y_{1,t} \colon 1, \ldots, T_1\}$} \label{uemshocktransience}
	\end{center}	
\end{figure}
